---
title: "LevelsClean"
author: "Uli Kaulfuss"
date: "5 Januar 2020"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, rows.print=25)
set.seed(42)

library(dplyr)
library(Hmisc)
library(readxl)
library(data.table)
library(sjlabelled)
library(e1071)
library(psych)
library(OneR)

```

# Objective

The following script uses the exported GEDA data from STATA and - based off the data dictionary - ensures correct factorization of the data including value and variable labeling incl. translation of the dataset.

To ensure that the script runs, download the required files from Googel drive and put them in the respective directories. 

## Processing

Loading the GEDA daat as it is exported from STATA with characters / strings as output format

```{r}

GEDA14_Export_text <- read_excel("data/GEDA14.Export.xlsx")

df_geda_de <- GEDA14_Export_text %>% dplyr::select(c(sex, GZmehm1, GZmehm3C, PAgroe))

```

Load meta data from the data dictionary as it has been prepared in XLS

```{r}
df_meta_lvls <- read_excel("data.doc/GEDA14_Variablenuebersicht_Analyse.xlsx", sheet='levels')

df_meta_lvls$numLevel <- as.numeric(df_meta_lvls$numLevel)

```

Loop through all columns and replace the texts from the STATA export with the levels from the data dictionary. "ORDINAL" factors need to be sorted correctly, this is ensured through the lookup table in the meta data

```{r}
df_geda_de <- GEDA14_Export_text # %>% dplyr::select(c(sex, GZmehm1, GZmehm3C, PAgroe, IAarzt1B4w))

df_geda_en <- copy(df_geda_de)
df_geda_num <- copy(df_geda_de)



for (i in colnames(df_geda_de)){
  
  col_meta <- df_meta_lvls[df_meta_lvls$Varname == i,]
  
  col_type <- col_meta[1,]$Type
  
  if(nrow(col_meta) > 0){
    
    print(paste("variable: ", i))
    
    if (col_type == 'Nominal' |col_type == 'Ordinal' ){
      
      unique_lvls <- unique(df_geda_de[[i]])
      
      for (l in unique_lvls){
        
        if (!is.na(l)){
          # print(paste(i, ": level: ", l))
          
          if (nrow(col_meta[col_meta$textLevel == l,]) > 0){
            df_geda_de[[i]][df_geda_de[[i]] == l] <- col_meta[col_meta$textLevel == l,]$numLevel
            
            df_geda_en[[i]][df_geda_en[[i]] == l] <- col_meta[col_meta$textLevel == l,]$numLevel
            df_geda_num[[i]][df_geda_num[[i]] == l] <- as.numeric(col_meta[col_meta$textLevel == l,]$numLevel)
            
          }else{
            
          }
          
        }
        
      }
      
      # for text columns, change data to factors 
      
      if (col_type == 'Nominal'){
        
        df_geda_de[[i]] <- factor(df_geda_de[[i]], levels=col_meta$numLevel, labels=col_meta$textLevel)
        df_geda_en[[i]] <- factor(df_geda_en[[i]], levels=col_meta$numLevel, labels=col_meta$textLabelEn)
        # df_geda_num[[i]] <- factor(as.numeric(df_geda_num[[i]]), levels=as.numeric(col_meta$numLevel), labels=col_meta$numLevel)
        
        
        

      }else if (col_type == 'Ordinal'){
        
        sort_order <- col_meta[1,]$SortOrder
        
        if(sort_order == "DESC"){
          df_geda_de[[i]] <- ordered(df_geda_de[[i]], levels=col_meta[order(-col_meta$numLevel),]$numLevel, labels=col_meta[order(-col_meta$numLevel),]$textLevel)
          df_geda_en[[i]] <- ordered(df_geda_en[[i]], levels=col_meta[order(-col_meta$numLevel),]$numLevel, labels=col_meta[order(-col_meta$numLevel),]$textLabelEn)
          # df_geda_num[[i]] <- ordered(as.numeric(df_geda_num[[i]]), levels=as.numeric(col_meta[order(-col_meta$numLevel),]$numLevel), labels=col_meta[order(-col_meta$numLevel),]$numLevel)
          
        }else{
          df_geda_de[[i]] <- ordered(df_geda_de[[i]], levels=col_meta[order(col_meta$numLevel),]$numLevel, labels=col_meta[order(col_meta$numLevel),]$textLevel)
          df_geda_en[[i]] <- ordered(df_geda_en[[i]], levels=col_meta[order(col_meta$numLevel),]$numLevel, labels=col_meta[order(col_meta$numLevel),]$textLabelEn)
          # df_geda_num[[i]] <- ordered(as.numeric(df_geda_num[[i]]), levels=as.numeric(col_meta[order(col_meta$numLevel),]$numLevel), labels=col_meta[order(col_meta$numLevel),]$numLevel)
        }
        
      }
      
    }else if (col_type == "Scale"){
      
      unique_lvls <- unique(col_meta)
      
      for (row_it in 1:nrow(col_meta)){
        
        l <- col_meta[row_it,]$textLevel
        
        if (!is.na(l) & l != ""){
          # print(paste(i, ": level: ", l))
        
          df_geda_de[[i]][df_geda_de[[i]] == l] <- col_meta[col_meta$textLevel == l,]$numLevel
          df_geda_en[[i]][df_geda_en[[i]] == l] <- col_meta[col_meta$textLevel == l,]$numLevel
          df_geda_num[[i]][df_geda_num[[i]] == l] <- as.numeric(col_meta[col_meta$textLevel == l,]$numLevel)
          
        }
        
      }
      
      # for scale columns, change datatype to numeric 
      df_geda_de[[i]]<- as.numeric(df_geda_de[[i]])
      df_geda_en[[i]]<- as.numeric(df_geda_en[[i]])
      # df_geda_num[[i]]<- as.numeric(df_geda_num[[i]])
      
    }
      # add variable label, access this with Hmisc-functions like describe(%dataframe%)
      
      label(df_geda_de[[i]]) <- col_meta[1,]$VarLabel
      label(df_geda_en[[i]]) <- col_meta[1,]$VarLabelEn
      label(df_geda_num[[i]]) <- col_meta[1,]$VarLabelEn
      
      
  }else{
    print(paste(i, ": type: ", col_type))
  }
  
}


```

Not only value labels have been added, also variable labels are now included so that the cryptic information is released to human readable text what each variable means. This can only be accessed by Hmisc functions as show below. Two dataframes incl. translated data are avaible and can be loaded for further processing. 

```{r}
describe(df_geda_de %>% dplyr::select(GZmehm1))

```

```{r}
describe(df_geda_en %>% dplyr::select(KHhyp))
```


```{r}
describe(df_geda_num %>% dplyr::select(KHhyp))
```
For those variables that contain +50 levels we decided to aggregate those variables into bins to facilitate the use of computational resources. Before binning the variables we debated any potential trade-off with the models predictive power. For example:

1) group the levels that have less than K observations into a new level called 'other'

2) run all the analysis using a subsample. It may be that there is not much difference in predictive power if you use a smaller sample, so you could do all the data mining cycle with less data and just train the final model with the entire sample (which may take a very long time, but you will only have to do that once)

3) use some feature selection technique (e.g. Lasso) after transforming the categorical features into binary features. That would tell you which levels are the less predictive (so you can group those levels together)

We concluded that we would aggregate / bin the variables based on #1. Rather than use K observations we relied on "business knowledge" to aggregate based on periods that made sense (e.g. if the data captures 30min increments, making it 1hr increments)


```{r}
#convert to numericals in order to plot
df_geda_num$KAtbka_k    <- as.numeric(df_geda_num$KAtbka_k)
df_geda_num$KAspodauC_k <- as.numeric(df_geda_num$KAspodauC_k)
df_geda_num$AUarbzD_k   <- as.numeric(df_geda_num$AUarbzD_k)
df_geda_num$IAkhs_k     <- as.numeric(df_geda_num$IAkhs_k)

#plot
barplot(table(df_geda_num$KAtbka_k))
barplot(table(df_geda_num$KAspodauC_k))
barplot(table(df_geda_num$AUarbzD_k))
barplot(table(df_geda_num$IAkhs_k))
```

```{r}

#Before binning we looked at the skewness of the data with the describe function to sanity check if we should "prioritize" certain transformations

#VARIABLE: KAtbka_k:
#Transportbez. körp. Aktivität in MET/Stunden/Woche (top coding ab 100h)
#Transportbez. körp. Activity in MET / hours / week (top coding from 100h)
breakpoint <- c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,40,42,44,46,48,102)
breakpoint_level_names <- c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,40,42,44,46,48)
describe(df_geda_num$KAtbka_k) #in order to measure skewness
df_geda_num$KAtbka_k <- cut(df_geda_num$KAtbka_k, breakpoint, labels = breakpoint_level_names, na.omit = FALSE)


#VARIABLE: KAspodauC_k
#Sport pro Woche insgesamt (in 30 min kategoriesiert)
#Sports week in total (category Siert in 30 min)
describe(df_geda_num$KAspodauC_k)
breakpoint_hour <- c(0,2,4,6,8,10,12,14,16,18,20,22,24,26,28,30,62)
breakpoint_hour_level_names <- c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15)
df_geda_num$KAspodauC_k <- cut(df_geda_num$KAspodauC_k,breakpoint_hour,labels = breakpoint_hour_level_names,ordered_result = TRUE, is.omit = FALSE)


#VARIABLE: AUarbzD_k
#Krankheitsbedingt nicht zur Arbeit: Wochen
#not due to illness to work: weeks
describe(df_geda_num$AUarbzD_k)
breakpoint_sick <- c(0,1,2,3,4,5,6,7,9,10,11,12,60)
breakpoint_sick_level_names <- c(0,1,2,3,4,5,6,7,9,10,11,12)
df_geda_num$AUarbzD_k <- cut(df_geda_num$AUarbzD_k,breakpoint_sick,labels = breakpoint_sick_level_names,ordered_result = TRUE, is.omit = FALSE)


#VARIABLE: IAkhs_k
#Stationär im Krankenhaus i.d.l. 12 Mon.: Anzahl der Nächte (kat)
#Stationary i.d.l. in hospital 12 month .: Number of nights (cat)
describe(df_geda_num$IAkhs_k)

### DID NOT BIN GIVEN ONLY ABOUT ~20 LEVELS WERE USED BY THE EXISTING VARIABLES ###

```

```{r}
#plot the binned variables
barplot(table(df_geda_num$KAtbka_k))
barplot(table(df_geda_num$KAspodauC_k))
barplot(table(df_geda_num$AUarbzD_k))
barplot(table(df_geda_num$IAkhs_k))
```

```{r}
save(df_geda_de, df_geda_en, df_geda_num, file = "data/geda_data.RData")
```

```{r}
write.csv(df_geda_num, "20012020_df_geda_num.csv")
```

